What do incoming university students believe about open science practices in

### 2021-03-09 analysis/Manuscript.Rmd
Working on differences in means

Of the remaining `r n` participants, most reported that they were
18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old. ADD GENDER HERE!

@@

## Data analysis
<!-- Can we move this to a reproducible code statement at the end? It works now -->

@@

>>>>

Of the remaining `r n` participants, most reported that they were
18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old.

<!-- ADD GENDER HERE! -->

@@

## Data analysis

```{r, difference between norm & counternorm, eval = FALSE}

# select all columns that relate to norms & counternorms
diff <- df %>% select(c(id, ends_with("norm")))

means <- diff %>% 
  sapply(mean, na.rm = TRUE)

knitr::kable(means)

# select columns that relate to norms
norms <- df %>% select(c(id, ends_with("_norm")))

# select columns that relate to counternorms
cnorms <- df %>% select(c(id, ends_with("_cnorm")))

# breadcrumbs - pivot long

norm_long <- norms %>% 
  pivot_longer (cols = ends_with("norm"),
                names_to = "practice",
                values_to = "rating") 
  str_remove(norm_long, "_norm")

norm_wide <- diff %>% 
  pivot_wider(names_from = ends_with("_norm"),
              values_from = c(ends_with("_norm"), ends_with("_cnorm"))
)
```

```{r, eval=FALSE}
# I'm sure there's a fancier way to subtract the counternorm from the norm, 
  # but for now we will do this...

norms <-  vars_select(names(df), ends_with('_norm'))
cnorms <-  vars_select(names(df), ends_with('_cnorm'))

miss_fun = function(x){
  sum(is.na(x))
}

diff_fun = function(x, y){
  (norms - cnorms)
}

diff_fun(x = norms, y = cnorms)

df$diff <- apply(X = df[, ], MARGIN = 1, FUN = miss_fun)

@@

\newpage
# Reproducible Code Statement
